---
title: "Biden Transition - Agency Review Teams"
author: "Aaron Kessler, Data/Investigations Team"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(janitor)
library(scales)
library(gt)
library(kableExtra)
options(dplyr.summarise.inform = FALSE)

#run the script for step 03 to update data files
# source("03_analysis.R")


#load data files from step 03
#entire combined agency teams file
agencyteams <- readRDS("processed_data/agencyteams.rds")
#names of new agency review team members
newnames <- readRDS("processed_data/newnames.rds")
#aggregate county of agency totals compared
agencycount_compare <- readRDS("processed_data/agencycount_compare.rds")


```

####
The following is an analysis based on scraping Joe Biden's presidential transition website to capture the various lists of members on the Agency Review Teams.  
  
The names below reflect the currently available data as of **`r format(Sys.time(), '%I:%M %p on %b. %d')`**.


####
### *New Names*

Here are the new names added to the agency review team lists since last time.  
Note that some people may already be part of another team and/or assigned to multiple agency teams - they're marked below as appropriate.  
  
  

```{r, echo=FALSE}

newnames %>% 
  select(agency, name, most_recent_employment, on_multiple_teams, team_lead) %>% 
  gt() %>%
  # tab_header(
  #   title = md("Ads Aired by **Party**"),
  #   subtitle = "(From Nov. 4th)"
  # ) %>% 
  tab_options(table.align = "left") %>%
  cols_align(
    align = "center",
    columns = vars(team_lead, on_multiple_teams)
  ) # %>%
  # fmt_number(
  #   columns = vars(ads_aired),
  #   decimals = 0,
  #   use_seps = TRUE
  # ) %>% 
  # fmt_currency(
  #   columns = vars(est_spent),
  #   decimals = 0,
  #   currency = "USD"
 

```


####
### *Aggregate Team Totals*

The number of people appointed to each agency team, along with change since last time reflecting the number of new people added. (Agencies with no change are omitted here.)
  

```{r, echo=FALSE}

agencycount_compare %>% 
  filter(change > 0) %>% 
  gt() %>%
  tab_options(table.align = "left") 
  # tab_header(
  #   title = md("Ads Aired by **Party**"),
  #   subtitle = "(From Nov. 4th)"
  # ) %>% 

  # cols_align(
  #   align = "center",
  #   columns = vars(team_lead, on_multiple_teams)
  # ) # %>%
  # fmt_number(
  #   columns = vars(ads_aired),
  #   decimals = 0,
  #   use_seps = TRUE
  # ) %>% 
  # fmt_currency(
  #   columns = vars(est_spent),
  #   decimals = 0,
  #   currency = "USD"
 

```





<!-- #### -->
<!-- ### *Daily Totals* -->
<!-- ```{r, echo=FALSE} -->

<!-- dailycount_byparty <- ga_runoff_tvads %>%  -->
<!--   count(airdate, advertiser_party, name = "ad_count") %>%  -->
<!--   # filter(airdate < "2020-11-23") -->

<!-- #area chart by party -->
<!-- ggplot(dailycount_byparty, aes(x = airdate, y = ad_count)) +  -->
<!--   geom_col(aes(color = advertiser_party, fill = advertiser_party),  -->
<!--             alpha = 0.5, position = position_dodge(preserve = "single")) + -->
<!--   scale_color_manual(values = c("#00AFBB", "#F2785D")) + -->
<!--   scale_fill_manual(values = c("#00AFBB", "#F2785D")) + -->
<!--   labs(title = "Daily Count of Ad Spots, By Party",  -->
<!--        subtitle = "", -->
<!--        x = "", -->
<!--        y = "") + -->
<!--   theme_minimal() + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + -->
<!--   scale_y_continuous(labels = comma) -->



<!-- ``` -->

<!-- #### -->
<!-- ```{r, echo=FALSE} -->

<!-- dailycount_bycand <- ga_runoff_tvads %>%  -->
<!--   count(airdate, advertiser, name = "ad_count") -->

<!-- #bar chart for CANDIDATES -->
<!-- ggplot(dailycount_bycand, aes(x = airdate, y = ad_count)) +  -->
<!--   geom_col(aes(color = advertiser, fill = advertiser),  -->
<!--            alpha = 0.5, position = position_dodge(preserve = "single")) + -->
<!--   # scale_color_manual(values = c("#DC3A3A", "#4BAFD8", "#E8857E", "#2E90B8")) + -->
<!--   # scale_fill_manual(values = c("#DC3A3A", "#4BAFD8", "#E8857E", "#2E90B8")) + -->
<!--   labs(title = "Daily Count of Ad Spots, By Candidate",  -->
<!--        subtitle = "", -->
<!--        x = "", -->
<!--        y = "") + -->
<!--   theme_minimal() + -->
<!--   theme(plot.title = element_text(hjust = 0.5)) + -->
<!--   scale_y_continuous(labels = comma) -->


<!-- ``` -->



<!-- ```{r, echo=FALSE} -->




<!-- ``` -->



<!-- ```{r, echo=FALSE} -->




<!-- ``` -->



